\Large \bf Frontrunning

### 2018-07-04 frontrunning/Latex/sections/paper.tex
[frontrunning] some on traditional frontrunning and introductory remarks

\subsection{What is frontrunning?} %Definition of frontrunning
%Traditional
%WRT blockchain and decentralization
\subsection{Miners and their power} 
%Transaction order, can be used for frontrunning

@@

% maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!

@@

\begin{itemize}
\item {\textbf{Miner Frontrunning.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity. In the Bancor model, essentially buy orders increase the price of the tokens while sell order decrease it. Since the Blockchain miners are the only parties who can decide on the order of transactions within a block, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise. For example, a miner learns about the pending \textit{buy} transaction of 1000 Ether, based on the Bancor design, if this transaction goes through, it causes the price of Ether to increase. So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it. So he would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether. Doing so, he would receive a better rate than other Bancor user, can sell the tokens he has received and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell hi tokens in front, if he sees a pending \textit{sell} transaction.

>>>>

\subsection{What is frontrunning?} %Definition of frontrunning
%Traditional
Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978cboe}
\end{quote} 
On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
\begin{quote}
it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote} 
% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.

%In actuality, front-running is more complex than this definition suggests. It encompasses at least three forms of conduct, each of which raises different regulatory and policy issues.9 They are: (1) trading by third parties who are tipped on an impending block trade ("tippee" trading); (2) transactions in which the owner or purchaser of the block trade itself engages in the offset- ting futures or options transaction as a means of "hedging" against price fluctuations caused by the block transaction ("self-front-running"); 1 ° and (3) transactions where a broker with knowledge of an impending customer block order trades ahead of that order for the broker's own profit ("trading ahead").
% from JerryWMarkhamFrontRunning.pdf

% More to read and add from : SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
% https://www.sec.gov/about/annual_report/1988.pdf

\textbf{Frontrunning in Blockchains}: The main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, everyone running a node of such blockchain could potentially have access to such information, hence it makes it much easier for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.

%WRT blockchain and decentralization
\subsection{Miners and their power}
%Transaction order, can be used for frontrunning

@@

% maybe inlcude 0xbitcoin ERC721 mineable tokens frontrunning!
% mint: https://etherscan.io/tx/0x9883bc3ad018fd2b649982f88fbad7dc5abcb8f11c4f1d87ef814ba30c2b3428

@@

\begin{itemize}
\item {\textbf{Miner Frontrunning.}} As mentioned, Bancor protocol uses an algorithm that automatically calculates the price of digital assets to provide better market liquidity. In the Bancor model, essentially buy orders increase the price of the tokens while sell order decrease it. Since the Blockchain miners are the only parties who can decide on the order of transactions within a block, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise. For example, a miner learns about the pending \textit{buy} transaction of 1000 Ether, based on the Bancor design, if this transaction goes through, it causes the price of Ether to increase. So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it. So he would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether. Doing so, he would receive a better rate than other Bancor user, can sell the tokens he has received and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction.
